### 2013-01-10 paper/cover_letter.tex
Final submitted to PLoS CB

We submit this manuscript entitled "Spatially explicit model of the lymphocyte diaspora in influenza-infected lung quantifies constraints of chemokine directed migration" for consideration of publication in PLoS Computational Biology.  We feel this work will be of interest to investigators modeling the immune response for the ultimate purpose of improving vaccine design.

Many insights have derived from modeling the immune response using differential equations (ODEs) and delay differential equations (DDEs) to simulate linear and non-linear components.  We have taken a different approach, using agent-based spatially-explicit modeling to examine the recruitment of antigen-specific T cells to influenza-infected foci in the lung during a primary immune response.   ODE and DDE models do not take spatial effects into account, but given that the search occurs within a very large uninfected tissue space, we felt the efficiency of this search, depending largely on chemokine signaling of infected regions, needed to be carefully examined.  We found that, similar to the highly efficient recruitment of precursor T cells to the lymph nodes, activated T cell search is indeed efficient, with one caveat applicable to large infected foci.  We wish to stimulate other investigators to use agent-based modeling to carefully examine other aspects of the immune response in a spatially explicit manner, thus improving the comprehensive models of the immune response. \\

@@

All authors have read and approved the manuscript.

>>>>

We resubmit this manuscript entitled "Spatially explicit model of the lymphocyte diaspora in influenza-infected lung reveals thresholds on chemokine directed migration" for consideration of publication in PLoS Computational Biology.  We would like to thank each of you for giving us the opportunity to improve our paper and resubmit it.  We would like to reiterate our thanks to our reviewers for giving us very constructive criticism that we believe has greatly improved the paper.  We still feel this work will be of interest to investigators modeling the immune response for the ultimate purpose of improving vaccine design.  \\

@@

In review we have noticed that our bibliography does not use annotated journal names, which seem to be the standard for PLoS CB.  We have {\em not} changed our bibliography as of yet as it was generated automatically using the Mendeley Desktop suite.  If this is an issue, we would be happy to return and reconstruct the references manually. \\

All authors have read and approved the revised manuscript.
